Appendix

### 2020-05-02 appendix/appendixV5.Rmd
Stars for P-Values.

# Needed packages
pkgs <- c('tidyverse', 'meta', 'metafor', 'readxl',
          'dmetar', 'knitr', 'gridGraphics', 'gridExtra','ggpubr','kableExtra','magick')

@@

aux = list(mod3, mod5, mod1) %>%
  map(~{
    left_join(coefs, .x) %>%
      mutate(model = ifelse(is.na(model), model[1], model)) 
  }) %>%
  reduce(bind_cols) %>%
  mutate(order = ifelse(` ` == "Intercept", 1, NA),
         order = ifelse(` ` == "Indepvar: N", 2, order),
         order = ifelse(` ` == "Indepvar: logN", 3, order),
         order = ifelse(` ` == "Year", 4, order),
         order = ifelse(` ` == "Published: No", 5, order),
         order = ifelse(` ` == "Elecsys: Non-Majoritarian", 6, order),
         order = ifelse(` ` == "Method: Panel", 7, order),
         order = ifelse(` ` == "Method: IV", 8, order),
         order = ifelse(` ` == "AggLevel: States", 9, order)
         ) %>%
  arrange(order) %>%
  select(-` 1`, -` 2`, -contains("model"), -order) %>%
  mutate(mod = "Base") %>%
  select(mod, everything())

aux2 = list(mod4, mod6, mod2) %>%
  map(~{
    left_join(coefs, .x) %>%
      mutate(model = ifelse(is.na(model), model[1], model)) 
  }) %>%
  reduce(bind_cols) %>%
  mutate(order = ifelse(` ` == "Intercept", 1, NA),
         order = ifelse(` ` == "Indepvar: N", 2, order),
         order = ifelse(` ` == "Indepvar: logN", 3, order),
         order = ifelse(` ` == "Year", 4, order),
         order = ifelse(` ` == "Published: No", 5, order),
         order = ifelse(` ` == "Elecsys: Non-Majoritarian", 6, order),
         order = ifelse(` ` == "Method: Panel", 7, order),
         order = ifelse(` ` == "Method: IV", 8, order),
         order = ifelse(` ` == "AggLevel: States", 9, order)
         ) %>%
  arrange(order) %>%
  select(-` 1`, -` 2`, -contains("model"), -order) %>%
  mutate(mod = "All Coefs") %>%
  select(mod, everything())

aux <- bind_rows(aux, aux2) %>%
  select(-contains("CI"),-`T`,-T1,-T2)

@@

## Summary of Results
```{r, echo=F, warning=F,error=F,message=F,asis=T}
kable(aux, 
      booktabs = T,
      longtable = F,
      align = "c",
      linesep ='',
      col.names = c(
        " ",
        " ",
        "Estimate",
        "SE",
        "P-Value",
        #
        "Estimate",
        "SE",
        "P-Value",
        #
        "Estimate",
        "SE",
        "P-Value"
      )) %>% 
  collapse_rows(
    1:2,
    row_group_label_position ='stack'
    ) %>%
  add_header_above(c(" ", " ","ExpPC" = 3, "logExpPC" = 3, "PCTGDP" = 3)) %>%
  kable_styling(
    c("striped",
      "bordered", 
      "scale_down",
      "repeat_header"
      ),
    position = "center",
    latex_options = c("repeat_header"))

@@

aux = list(mod3_permu, mod5_permu, mod1_permu) %>%
  map(~{
    left_join(coefs, .x) %>%
      mutate(model = ifelse(is.na(model), model[1], model)) 
  }) %>%
  reduce(bind_cols) %>%
  mutate(order = ifelse(` ` == "Intercept", 1, NA),
         order = ifelse(` ` == "Indepvar: N", 2, order),
         order = ifelse(` ` == "Indepvar: logN", 3, order),
         order = ifelse(` ` == "Year", 4, order),
         order = ifelse(` ` == "Published: No", 5, order),
         order = ifelse(` ` == "Elecsys: Non-Majoritarian", 6, order),
         order = ifelse(` ` == "Method: Panel", 7, order),
         order = ifelse(` ` == "Method: IV", 8, order),
         order = ifelse(` ` == "AggLevel: States", 9, order)
         ) %>%
  arrange(order) %>%
  select(-` 1`, -` 2`, -contains("model"), -order) %>%
  mutate(mod = "Base") %>%
  select(mod, everything())

aux2 = list(mod4_permu, mod6_permu, mod2_permu) %>%
  map(~{
    left_join(coefs, .x) %>%
      mutate(model = ifelse(is.na(model), model[1], model)) 
  }) %>%
  reduce(bind_cols) %>%
  mutate(order = ifelse(` ` == "Intercept", 1, NA),
         order = ifelse(` ` == "Indepvar: N", 2, order),
         order = ifelse(` ` == "Indepvar: logN", 3, order),
         order = ifelse(` ` == "Year", 4, order),
         order = ifelse(` ` == "Published: No", 5, order),
         order = ifelse(` ` == "Elecsys: Non-Majoritarian", 6, order),
         order = ifelse(` ` == "Method: Panel", 7, order),
         order = ifelse(` ` == "Method: IV", 8, order),
         order = ifelse(` ` == "AggLevel: States", 9, order)
         ) %>%
  arrange(order) %>%
  select(-` 1`, -` 2`, -contains("model"), -order) %>%
  mutate(mod = "All Coefs") %>%
  select(mod, everything())

aux <- bind_rows(aux, aux2) %>%
  select(-contains("CI"),-`T`,-T1,-T2)

@@

## Summary of Results (Permutation)
```{r, echo=F, warning=F,error=F,message=F,asis=T}
kable(aux, 
      "latex",
      booktabs = T,
      longtable = F,
      align = "c",
      linesep ='',
      col.names = c(
        " ",
        " ",
        "Estimate",
        "SE",
        "P-Value",
        #
        "Estimate",
        "SE",
        "P-Value",
        #
        "Estimate",
        "SE",
        "P-Value"
      )) %>% 
  collapse_rows(
    1:2,
    row_group_label_position ='stack'
    ) %>%
  add_header_above(c(" ", " ","ExpPC" = 3, "logExpPC" = 3, "PCTGDP" = 3)) %>%
  kable_styling(
    c("striped",
      "bordered", 
      "scale_down",
      "repeat_header"
      ),
    position = "center",
    latex_options = c("repeat_header"))

>>>>

# Needed packages
pkgs <- c('tidyverse', 'meta', 'metafor', 'readxl',
          'knitr', 'gridGraphics', 'gridExtra','ggpubr','kableExtra','magick')

@@

aux = list(mod3, mod5, mod1) %>%
  map(~{
    left_join(coefs, .x) %>%
      mutate(model = ifelse(is.na(model), model[1], model)) 
  }) %>%
  reduce(bind_cols) %>%
  mutate(order = ifelse(` ` == "Intercept", 1, NA),
         order = ifelse(` ` == "Indepvar: N", 2, order),
         order = ifelse(` ` == "Indepvar: logN", 3, order),
         order = ifelse(` ` == "Year", 4, order),
         order = ifelse(` ` == "Published: No", 5, order),
         order = ifelse(` ` == "Elecsys: Non-Majoritarian", 6, order),
         order = ifelse(` ` == "Method: Panel", 7, order),
         order = ifelse(` ` == "Method: IV", 8, order),
         order = ifelse(` ` == "AggLevel: States", 9, order),
         pval = ifelse(`P-Value` < 0.05, "*", NA),
         pval = ifelse(`P-Value` < 0.01, "**", pval),
         pval = ifelse(`P-Value` < 0.01, "***", pval),
         pval = ifelse(`P-Value` >= 0.05, " ", pval),
         `P-Value` = pval) %>%
  arrange(order) %>%
  select(-` 1`, -` 2`, -contains("model"), -order) %>%
  mutate(mod = "Base") %>%
  select(mod, everything())

aux2 = list(mod4, mod6, mod2) %>%
  map(~{
    left_join(coefs, .x) %>%
      mutate(model = ifelse(is.na(model), model[1], model)) 
  }) %>%
  reduce(bind_cols) %>%
  mutate(order = ifelse(` ` == "Intercept", 1, NA),
         order = ifelse(` ` == "Indepvar: N", 2, order),
         order = ifelse(` ` == "Indepvar: logN", 3, order),
         order = ifelse(` ` == "Year", 4, order),
         order = ifelse(` ` == "Published: No", 5, order),
         order = ifelse(` ` == "Elecsys: Non-Majoritarian", 6, order),
         order = ifelse(` ` == "Method: Panel", 7, order),
         order = ifelse(` ` == "Method: IV", 8, order),
         order = ifelse(` ` == "AggLevel: States", 9, order),
         pval = ifelse(`P-Value` < 0.05, "*", NA),
         pval = ifelse(`P-Value` < 0.01, "**", pval),
         pval = ifelse(`P-Value` < 0.01, "***", pval),
         pval = ifelse(`P-Value` >= 0.05, " ", pval),
         `P-Value` = pval) %>%
  arrange(order) %>%
  select(-` 1`, -` 2`, -contains("model"), -order) %>%
  mutate(mod = "All Coefs") %>%
  select(mod, everything())

aux <- bind_rows(aux, aux2) %>%
  select(-contains("CI"),-`T`,-T1,-T2,-pval)

@@

## Summary of Results
```{r, echo=F, warning=F,error=F,message=F,asis=T}
kable(aux, 
      booktabs = T,
      longtable = F,
      align = "c",
      linesep ='',
      col.names = c(
        " ",
        " ",
        "Estimate",
        "SE",
        "P-Value",
        #
        "Estimate",
        "SE",
        "P-Value",
        #
        "Estimate",
        "SE",
        "P-Value"
      )) %>% 
  collapse_rows(
    1:2,
    row_group_label_position ='stack'
    ) %>%
  add_header_above(c(" ", " ","ExpPC" = 3, "logExpPC" = 3, "PCTGDP" = 3)) %>%
  kable_styling(
    c("striped",
      "bordered", 
      "scale_down",
      "repeat_header"
      ),
    position = "center",
    latex_options = c("repeat_header")) %>%
  footnote(general = "Signif. codes:  0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1")

@@

aux = list(mod3_permu, mod5_permu, mod1_permu) %>%
  map(~{
    left_join(coefs, .x) %>%
      mutate(model = ifelse(is.na(model), model[1], model)) 
  }) %>%
  reduce(bind_cols) %>%
  mutate(order = ifelse(` ` == "Intercept", 1, NA),
         order = ifelse(` ` == "Indepvar: N", 2, order),
         order = ifelse(` ` == "Indepvar: logN", 3, order),
         order = ifelse(` ` == "Year", 4, order),
         order = ifelse(` ` == "Published: No", 5, order),
         order = ifelse(` ` == "Elecsys: Non-Majoritarian", 6, order),
         order = ifelse(` ` == "Method: Panel", 7, order),
         order = ifelse(` ` == "Method: IV", 8, order),
         order = ifelse(` ` == "AggLevel: States", 9, order),
         pval = ifelse(`P-Value` < 0.05, "*", NA),
         pval = ifelse(`P-Value` < 0.01, "**", pval),
         pval = ifelse(`P-Value` < 0.01, "***", pval),
         pval = ifelse(`P-Value` >= 0.05, " ", pval),
         `P-Value` = pval) %>%
  arrange(order) %>%
  select(-` 1`, -` 2`, -contains("model"), -order) %>%
  mutate(mod = "Base") %>%
  select(mod, everything())

aux2 = list(mod4_permu, mod6_permu, mod2_permu) %>%
  map(~{
    left_join(coefs, .x) %>%
      mutate(model = ifelse(is.na(model), model[1], model)) 
  }) %>%
  reduce(bind_cols) %>%
  mutate(order = ifelse(` ` == "Intercept", 1, NA),
         order = ifelse(` ` == "Indepvar: N", 2, order),
         order = ifelse(` ` == "Indepvar: logN", 3, order),
         order = ifelse(` ` == "Year", 4, order),
         order = ifelse(` ` == "Published: No", 5, order),
         order = ifelse(` ` == "Elecsys: Non-Majoritarian", 6, order),
         order = ifelse(` ` == "Method: Panel", 7, order),
         order = ifelse(` ` == "Method: IV", 8, order),
         order = ifelse(` ` == "AggLevel: States", 9, order),
         pval = ifelse(`P-Value` < 0.05, "*", NA),
         pval = ifelse(`P-Value` < 0.01, "**", pval),
         pval = ifelse(`P-Value` < 0.01, "***", pval),
         pval = ifelse(`P-Value` >= 0.05, " ", pval),
         `P-Value` = pval) %>%
  arrange(order) %>%
  select(-` 1`, -` 2`, -contains("model"), -order) %>%
  mutate(mod = "All Coefs") %>%
  select(mod, everything())

aux <- bind_rows(aux, aux2) %>%
  select(-contains("CI"),-`T`,-T1,-T2,-pval)

@@

## Summary of Results (Permutation)
```{r, echo=F, warning=F,error=F,message=F,asis=T}
kable(aux, 
      booktabs = T,
      longtable = F,
      align = "c",
      linesep ='',
      col.names = c(
        " ",
        " ",
        "Estimate",
        "SE",
        "P-Value",
        #
        "Estimate",
        "SE",
        "P-Value",
        #
        "Estimate",
        "SE",
        "P-Value"
      )) %>% 
  collapse_rows(
    1:2,
    row_group_label_position ='stack'
    ) %>%
  add_header_above(c(" ", " ","ExpPC" = 3, "logExpPC" = 3, "PCTGDP" = 3)) %>%
  kable_styling(
    c("striped",
      "bordered", 
      "scale_down",
      "repeat_header"
      ),
    position = "center",
    latex_options = c("repeat_header")) %>%
  footnote(general = "Signif. codes:  0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1")
